Model Checking Differentially Private Properties

### 2018-08-21 main.tex
add authers and institutes

\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{xspace}
\pagestyle{plain}
\usepackage{multirow}
\usepackage{algorithm,algpseudocode}
\usepackage{caption}
\usepackage{subcaption}
\captionsetup{compatibility=false}
\usepackage{wrapfig}
\usepackage{mathtools}
\usepackage{tikz}
\usetikzlibrary{arrows,calc}
\usepackage{url}
\usepackage{times}

@@

\newif\ifpublic
%\publictrue

\title{Model Checking Differentially Private Properties}
\ifpublic
\author{
Depeng Liu\inst{1}
\and
Bow-Yaw Wang\inst{2}
\and
Lijun Zhang\inst{1}}
\institute{
Chinese Academy of Sciences
\and
Academia Sinica
}
\else
\author{Author}
\institute{Institute}
\fi

@@

>>>>

\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{xspace}
\pagestyle{plain}
\usepackage{multirow}
\usepackage{algorithm,algpseudocode}
\usepackage{caption}
\usepackage{subcaption}
\captionsetup{compatibility=false}
\usepackage{wrapfig}
\usepackage{mathtools}
\usepackage{tikz}
\usetikzlibrary{arrows,calc}
\usepackage{url}
\usepackage{times}
\usepackage[symbol]{footmisc}
\renewcommand{\thefootnote}{\fnsymbol{footnote}}

@@

\newif\ifpublic
\publictrue

\title{Model Checking Differentially Private Properties}
\ifpublic
\author{
Depeng Liu\inst{1,2}
\and
Bow-Yaw Wang\inst{3}
\and
Lijun Zhang\inst{1,2}}
\institute{
State Key Laboratory of Computer Science, Institute of Software,
Chinese Academy of Sciences
\footnotemark[1]
\and
University of Chinese Academy of Sciences
\footnotemark[1]
\and
Institute of Information Science, Academia Sinica
\footnotemark[2]
}
\else
\author{Author}
\institute{Institute}
\fi

@@

\footnotetext[1]{Partially supported by \todo{please fill in}}
\footnotetext[2]{Partially supported by the Academia
Sinica Thematic Project: Socially Accountable Privacy Framework for
Secondary Data Usage.}
